%!TEX root = ../report.tex

\begin{document}
	\chapter{Conclusions}
	Many aspects of the real-world data are indexed by time; thus, analyzing the time series data has become an essential research problem. To better understand the real-world data, the first and most relevant approach is exploring the domain knowledge. The problem with this method is that it cannot be generalized and requires a relevant skillset in the domain. Hence unsupervised algorithms were applied to solve this problem. This work focuses on exploring methods that can be applied for feature extraction of the real-world complex industrial dataset.
	
	To understand the complex data, domain-specific knowledge such as temporal, spectral, and statistical is first explored. As observed, prior domain knowledge highly influences the classification task. Therefore, state-of-the-art supervised and unsupervised learning algorithms have been surveyed to identify suitable approaches to automate the process. The first unsupervised approach applied to the problem is reconstruction-based anomaly detection. This method uses reconstruction error as a threshold to differentiate anomalous data from normal. However, due to the lower number of instances and highly imbalanced data, the deep learning algorithm fails to detect the anomaly. An important observation made in experimentation is that it is difficult to differentiate between positive and negative instances as they are very similar. 
	To solve the issues in this method, a transfer learning approach was implemented based on \cite{fawaz2018transfer}. However, this technique also fails to identify negative instances, a possible reason being the source and target domains are not similar enough.
	
	Thus to increase the features, space image transformation is applied that is by converting the raw signal to spectrograms. The computer vision-based transfer-learning method is applied to the problem. Due to the complexity of training VGG model and some challenges faced by spectrogram transfer learning using CNN the algorithm does not identify negative instances.
	
	To remove redundant data and retain critical information from spectrogram, autoencoder based feature extraction technique is applied to data. This method also fails to contribute to the classification of the feature set.
	
	To conclude, due to highly imbalanced and complex data, domain knowledge works better a detecting abnormal data after applying some data balancing methods. The deep-learning models need a large amount of data for training efficiency.
	
	
	
	
	\section{Contributions}
	\begin{itemize}
		\item Survey of the supervised and unsupervised state of the art feature extraction algorithms for time-series data
		\item Data analysis of a complex industrial dataset.
		\item Implementation and evaluation of domain-based feature extraction method to analyze time-series data.
		\item Implementation and evaluation of reconstruction error-based anomaly detection method.
		\item Implementation of method that uses features from both time and frequency domain, that is, using spectrograms.
		\item Feature extraction using of state of the art transfer learning technique.
	\end{itemize}
	
	
	\section{Lessons learned}
	\begin{itemize}
		\item The performance is affected by an imbalance in data.
		\item The dataset is built upon just a single acceleration signal and the features that are extracted from it. Thus the domain knowledge is also limited.
		\item Domain-specific knowledge plays an important role in the performance of the model.
		\item Spectrogram approach is not suitable for an industrial dataset in use which can be analyzed from the results of both transfer learning and autoencoder-based feature extraction model.
		\item Based on the reconstruction error of the anomaly detection module, the features of the data that differentiate abnormal behavior from normal are not that prominent.
		\item Domain-based feature extraction is best suitable for this problem.
	\end{itemize}
	
	\section{Future work}
	The future scope of this work is as follows:
	\begin{itemize}
		\item As we have observed, negative instance detection is highly dependent on penetration a maximum velocity which is marked by point changes in the position and velocity signal, respectively. Thus changepoint algorithms can be applied for feature extraction.
		\item Convolution neural networks and relevant trainable filters can be used to extract the temporal features of time series data. 
		
	\end{itemize}
\end{document}
